\domingo{Advances in wireless comunication and signal proccesing have drastically changed the capabilities of transmitting information.}
\domingo{\textit{Comentario: El siguiente párrafo lo deberías reescribir un poco, para ser más específico al trabajo. Internet está formado por varias redes y no tiene que ver en este caso aunque todo use señales. Intenta ser especifico porque publicar es mas un tema de servidores web que de comunicaciones}}
Physical maps have lost relevance long ago in favor of real-time position
tracking systems. Who needs a physical meter when you can send a signal to
measure distances \domingo{accurately}?. Thanks to the hard work of engineers that squeeze
the capabilities of the carrier wave to transport information throughout 
\domingo{ different networks}, we can even \doming{read} this document \domingo{in our browser}.\\

\domingo{\textit{Comentario: Escribir un párrafo para enlazar sobre que las secuencias con buenas propiedades se requieren en muchos casos. Para dar un par de ejemplos, nos centraremos en dos tecnologias : tecnicas de espectro ensanchado (spread-spectrum) y por otro lado tecnicas de localización (rádar). He pasado lo de las lineas 155- 158 aqui para hablar de aplicaciones.}}
\begin{outline}
  \1 As the spreading code in direct-sequence spread spectrum(DSSS) \cite{DSSS_1}\cite{DSSS}
    \2 CDMA in wireless communication\cite{DSSS}
  \1 PRN-based radars\cite{prn_radar_example1}\cite{prn_radar_example2}
    \2 GPS\cite{GPS}
\end{outline}



\domingo{Spread-spectrum systems originated in military applications in order to provide capability for anti-jamming,  low probability of interception and  to make multiple users sharing a common channel possible (the so-called code-division multiple access (CDMA)).  The most popular application were in 3G mobile cell communications, but also it is avaliable in  ultra-wideband (UWB) and  networks developed for law enforcement agencies can choose spread spectrum due to their security ( citar Communication systems securtity, cheng, Gong). The downside is that it is not as efficient in terms of bandwidth required to send the information. Spread-spectrum signals have several forms in direct sequence (DS), frequency hopping (FH), and time hopping.}
 
\domingo{\texit{El capitulo 15 del libro de Gong sobre seguridad lo dedica a explicar porque estas tecnicas son más seguras ante atacantes que quieran escuchar con su propia antena o emitir interferencias para que nadie pueda comunicarse en ese canal. Es una las razones de la popularidad de estas secuencias. UWB es similar a Wifi, no requiere licencia para ponerte tener tu red inalámbrica y se suele utilizar para aplicaciones de sensores, localización y similares, que requieran poca velocidad de transmision. Esto es solo para que lo conozcas por encima.  DS, FH, Time hopping sólo tienes que saber que son distintas formas de utilizar la secuencia para separar los usuarios la primera es por código ortogonal pero tambien se puede hacer en frecuencia y en tiempo usando las secuencias de otra manera, puedes expandirlo un poco si quieres para explicar esto.}}


\domingo{ \textit{ESTO REESCRIBELO EN TUS PALABRAS Y ENLAZALO CON TU SECCION DE PN} Spreading sequences, generated by a pseudo-noise (PN) generator, used in spread- spectrum systems are pseudorandom sequences with good correlation. Especially m-sequences have been widely used in digital communications for more than 60 years, because their autocorrelation resembled white Gaussian noise processes, from which the name “pseudo- noise” comes.
Spreading is accomplished by means of a spreading sequence (or code) that is pre-shared for generation of employed pseudo- random noise (PN) sequences, which is independent of the data, called spreading sequences or chip sequences or signature sequences in different applications. 
 At the receiver, despreading (recover- ing the original data) is accomplished by the correlation of the received spread signal with a synchronized replica of the spreading sequence used to spread the information. } 
 


\domingo{A radar (radio detection and ranging) uses a radio-frequency electromagnetic signal reflected from a target to determine properties such as position, speed, etc
\textit{ Comentario:Esto hay que expandirlo pero solo explicarlo muy por encima, hay que mencionar en que se basa el radar, porque son interesantes las secuencias}
} 

\domingo{\textit{Comentario: Añade aqui algo sobre GPS, porque luego lo mencionas . Una buena referencia es: Ipatov, V. P., & Shebshayevic, B. V. (2010). Some proposals on signal formats for future GNSS air interface. Inside GNSS. Está en mendeley}.
Global possitining system is a satellite -based radionavigation owned by the United States offering geolocalization and time possitioning. They broadcast a current time and their position, using a binary sequence for synchronization. Because the wave speed is constant, the distance to an emitting satellite can be calculated and, together with the distance to three other satellite, the position of the reciever can be found solving a simple linear algebra system.
}


In this chapter, we will introduce the  auto and crosscorrelation function for periodic binary sequences and its mathematical
properties. We will also take a look at pseudorandom sequences, its properties and
practical applications.

 \input{Chapters/Introduction/functions.tex}
